### 2024-10-22 analysis/preprocessing.qmd
arousal analysis included
feat(preprocessing): update R_studies build
Drop resonance(deng2015em), tension arousal (wang2022cr, wang2021ac), Remove NAs from values column (zhang2017fe, zhang2016br, gingras2014be). Fix unique_ids for hu2016cr

@@

@@

```{r}
R_studies$dimension[str_detect(R_studies$dimension,'activation|energy arousal|tension arousal')]<-'arousal'
R_studies$dimension[str_detect(R_studies$dimension,'pleasantness')]<-'valence'
R_studies <- dplyr::filter(R_studies,!str_detect(dimension,'av|resonance')) # relates to distances, can be omitted

@@

g1
```
## Select a summary measure for valence and arousal separately

@@

R_studies$feature_n[str_detect(R_studies$feature_n,'pre_fitting = 21')] <- 21
R_studies$feature_n[str_detect(R_studies$feature_n,'548 dimensions')] <- 548
R_studies$feature_n[str_detect(R_studies$feature_n,'548; after reduct')] <- 548
R_studies$feature_n[str_detect(R_studies$feature_n,'60 handcrafted and filter bank')] <- 3600
R_studies$feature_n[str_detect(R_studies$feature_n,'Features deep-learned from audio (not specified) but 1802 in DEAM')] <- 260

R_studies$feature_n[str_detect(R_studies$feature_n,'not specified')] <- 3000 # under-estimation based openSmile features and the paper arguing that they have 15 stat moments

@@

table(R_studies$feature_n_complexity)
```
## Feature N and genre split

>>>>

```
2024-10-21: Update studies with multiple unique_ids due to multiple stats reported
```{r}
metaMER_results <- metaMER_results |> 
  dplyr::filter(!(citekey == "zhang2017fe" & statistic == "mean"),
         !(citekey == "zhang2016br" & statistic == "mean"),
         !(citekey == "zhang2016br" & is.na(values)),
         !(citekey == "coutinho2017sh" & statistic == "ccc"),
         # Include only results for energy arousal
         !(citekey == "wang2022cr" & dimension == "tension arousal"),
         !(citekey == "wang2021ac" & dimension == "tension arousal"),
         !(citekey == "deng2015em" & dimension == "resonance"))
```
Deal with repeated experiment IDs in `hu2017cr`
```{r}

# get citation keys (all currently say experiment 1)
hu2017models <- metaMER_results[str_detect(metaMER_results$citekey, 
                                           "hu2017cr"),]$unique_id

# replace the last digit with 1:4 (representing each experiment)
hu2017models_replacement <- paste0(
substr(hu2017models, 
       1, 
       nchar(hu2017models) - 1),
1:4
)

# overwrite original values
metaMER_results[metaMER_results$unique_id %in% 
                  hu2017models,]$unique_id <- hu2017models_replacement
```

@@

```
## Remove NAs

```{r}
R_studies <- R_studies[!is.na(R_studies$values),]

## Check models aren't double-counted

```{r}
length(unique(paste0(R_studies$unique_id, R_studies$dimension)))

ez::ezDesign(data = R_studies, x = unique_id, y = citekey)

@@

```{r}
R_studies$dimension[str_detect(R_studies$dimension,'activation|energy arousal|tension arousal')]<-'arousal' # note: there is no longer "tension arousal" based on decision to include only energy
R_studies$dimension[str_detect(R_studies$dimension,'pleasantness')]<-'valence'
R_studies <- dplyr::filter(R_studies,!str_detect(dimension,'av|resonance')) # relates to distances, can be omitted

@@

## Feature N and genre split

@@

R_studies$feature_n[str_detect(R_studies$feature_n,'150 PCA features')] <- 3000
R_studies$feature_n[str_detect(R_studies$feature_n,'pre_fitting = 21')] <- 21
R_studies$feature_n[str_detect(R_studies$feature_n,'548 dimensions')] <- 548
R_studies$feature_n[str_detect(R_studies$feature_n,'548; after reduct')] <- 548
R_studies$feature_n[str_detect(R_studies$feature_n,'60 handcrafted and filter bank')] <- 3600
R_studies$feature_n[str_detect(R_studies$feature_n,'Features deep-learned from audio (not specified) but 1802 in DEAM')] <- 260

# 2024-10-21: I changed the encoding for this one to "150 PCA features", so updated above.
# R_studies$feature_n[str_detect(R_studies$feature_n,'not specified')] <- 3000 # under-estimation based openSmile features and the paper arguing that they have 15 stat moments

@@

table(R_studies$feature_n_complexity)
```

## Feature N and genre split
